Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-05 awipev-CO2.Rmd
Changed info on server and on-going work on data availability

```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
selected_nydata_minute <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_minute.rds")) %>%
  dplyr::select(ends_with("_qf")) #%>%
# s1 <- summary(as.factor(selected_nydata_minute$pco2_corr_qf))*100/length(selected_nydata_minute$pco2_raw_qf)
# s2 <- summary(as.factor(selected_nydata_minute$sal_fb_qf))*100/length(selected_nydata_minute$sal_fb_qf)
# s3 <- summary(as.factor(selected_nydata_minute$sal_insitu_ctd_qf))*100/length(selected_nydata_minute$sal_insitu_ctd_qf)
# s4 <- summary(as.factor(selected_nydata_minute$temp_dur_qf))*100/length(selected_nydata_minute$temp_dur_qf)
# s5 <- summary(as.factor(selected_nydata_minute$temp_fb_qf))*100/length(selected_nydata_minute$temp_fb_qf)
# s6 <- summary(as.factor(selected_nydata_minute$temp_insitu_11m_qf))*100/length(selected_nydata_minute$temp_insitu_11m_qf)
# s7 <- summary(as.factor(selected_nydata_minute$phINT_qf))*100/length(selected_nydata_minute$phINT_qf)
# s8 <- summary(as.factor(selected_nydata_minute$phEXT_qf))*100/length(selected_nydata_minute$phEXT_qf)
# qflags <- tibble(pco2_corr = s1,
#                  sal_fb = s2,
#                  sal_insitu_ctd = s3,
#                  temp_dur = s4,
#                  temp_fb = s5,
#                  temp_insitu_11m = s6,
#                  phINT = s7,
#                  phEXT = s8)
#   
#   summarise_all(percentcumsum)
#   dplyr::mutate_all(funs("percent"= cumsum(.)/100))
# p <-  ggplot(data = selected_nydata_minute) +
#   geom_bar(aes(x = as.factor(pco2_corr_qf)))
# p
# rm(selected_nydata_minute)
```

@@

* (At 01:00, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
    + 00 01 * * * cd ; R \-\-vanilla < ny-alesund/R/ny-alesund_cc.R 
* (At 03:00, web page is generated)
    + 00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1  
* (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud ... Exp168)
    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
* (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)
    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'

>>>>

```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# function to express the number of quality flag in pefrcent for each variable
qflag <- function(x) {
  summary(as.factor(x))*100/length(x)
}
selected_nydata_minute <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_minute.rds")) %>%
dplyr::select(ends_with("_qf"), -dt_qf) 
nam <- selected_nydata_minute %>% names()
selected_nydata_minute %>% map(~qflag(.x))

s1 <- summary(as.factor(selected_nydata_minute$pco2_corr_qf))*100/length(selected_nydata_minute$pco2_corr_qf)
s2 <- summary(as.factor(selected_nydata_minute$sal_fb_qf))*100/length(selected_nydata_minute$sal_fb_qf)
s3 <- summary(as.factor(selected_nydata_minute$sal_insitu_ctd_qf))*100/length(selected_nydata_minute$sal_insitu_ctd_qf)
s4 <- summary(as.factor(selected_nydata_minute$temp_dur_qf))*100/length(selected_nydata_minute$temp_dur_qf)
s5 <- summary(as.factor(selected_nydata_minute$temp_fb_qf))*100/length(selected_nydata_minute$temp_fb_qf)
s6 <- summary(as.factor(selected_nydata_minute$temp_insitu_11m_qf))*100/length(selected_nydata_minute$temp_insitu_11m_qf)
s7 <- summary(as.factor(selected_nydata_minute$phINT_qf))*100/length(selected_nydata_minute$phINT_qf)
s8 <- summary(as.factor(selected_nydata_minute$phEXT_qf))*100/length(selected_nydata_minute$phEXT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s6,s7,s8))
colname(z) <- nam

qflag <- function(x) {
  summary(as.factor(x))*100/length(x)
}
qflags <- tibble(pco2_corr = s1,
                 sal_fb = s2,
                 sal_insitu_ctd = s3,
                 temp_dur = s4,
                 temp_fb = s5,
                 temp_insitu_11m = s6,
                 phINT = s7,
                 phEXT = s8)

  summarise_all(percentcumsum)
  dplyr::mutate_all(funs("percent"= cumsum(.)/100))
p <-  ggplot(data = selected_nydata_minute) +
  geom_bar(aes(x = as.factor(pco2_corr_qf)))
p
# rm(selected_nydata_minute)
```

@@

* (Every hour on the hour, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
    + 00 *//1 * * * cd $HOME; USER=awipev R --vanilla < ny-alesund/R/ny-alesund_cc.R > ny-alesund/R/log_ny-alesund_cc.txt 2>&1
* (Every hour at 10 min past the hour, the web page is generated)
    + 10 *//1 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1  
* (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud ... Exp168)
    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
* (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)
    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
